% gm-termtest-C-mock.tex

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\begin{document}

\textbf{Term Test C Exercises}

1. Identify the required features of the following conic sections
(parabola: vertex; ellipse: centre and dimensions; circle: centre and
radius; hyperbola: centre, dimensions, asymptotes).

% 8
\begin{equation}
  \label{eq:ohdiedoe}
4x^{2}-9y^{2}-8x-198y=1049
\end{equation}

% 6
\begin{equation}
  \label{eq:mahbeizo}
4y^{2}+80y+384=-x^{2}
\end{equation}

% 4
\begin{equation}
  \label{eq:ohwoojie}
16x(x+1)+8y(2y+3)=131
\end{equation}

% 7
\begin{equation}
  \label{eq:chohtohk}
x^{2}-y^{2}+4x+6y=6
\end{equation}

% 2
\begin{equation}
  \label{eq:gofushoo}
y(y-4)-x=2
\end{equation}

% 1
\begin{equation}
  \label{eq:vibeibie}
3x^{2}+\sqrt{252}x-y+23=0
\end{equation}

% 3
\begin{equation}
  \label{eq:aepheipi}
x^{2}+y^{2}-8x+6y=(\pi-5)(\pi+5)
\end{equation}

% 5
\begin{equation}
  \label{eq:vogeobab}
x^{2}+4y^{2}-2x+24y+33=0
\end{equation}

2. Simplify the following expressions.
% James Stewart, page 42
\begin{equation}
  \label{eq:uxohjeib}
\frac{2x^{3}-x^{2}-6x}{2x^{2}-7x+6}
\end{equation}
\begin{equation}
  \label{eq:eicohrae}
\frac{1-x^{2}}{x^{2}-1}
\end{equation}
\begin{equation}
  \label{eq:epuufeca}
\frac{x^{2}-x-6}{x^{2}+2x}\cdot\frac{x^{3}+x^{2}}{x^{2}-2x-3}
\end{equation}
\begin{equation}
  \label{eq:weungodu}
\frac{\frac{x^{3}}{x+1}}{\frac{x}{x^{2}+2x+1}}
\end{equation}
\begin{equation}
  \label{eq:oraighah}
\frac{1}{x+1}+\frac{1}{x-1}
\end{equation}
\begin{equation}
  \label{eq:saenonge}
\frac{5}{2x-3}-\frac{3}{(2x-3)^{2}}
\end{equation}
\begin{equation}
  \label{eq:eeghoghi}
1+\frac{1}{1+\frac{1}{1+x}}
\end{equation}
\begin{equation}
  \label{eq:eesicaet}
\frac{x}{x^{2}+x-2}-\frac{2}{x^{2}-5x+4}
\end{equation}
\begin{equation}
  \label{eq:fixahfee}
\sqrt{1+\left(x^{3}-\frac{1}{4x^{3}}\right)^{2}}
\end{equation}

3. Follow the word problems.

(a) Determine the angle between these two vectors.

\begin{equation}
  \label{eq:acaewoow}
a=\left(
  \begin{array}{c}
    0.05 \\
    0.12
  \end{array}\right)\mbox{ and }
b=\left(
  \begin{array}{c}
    -503 \\
    34
  \end{array}\right)
\end{equation}

(b) X walks 5km N$43^{\circ}$E, Y walks 7km S$81^{\circ}$W. Then Y
sends messenger Z to X with a message. Identify the vector which
corresponds to Z's route in kilometres. How far does Z need to go?

(c) Alexander van der Bellen walks along vector $a$ from $P$ to $Q$
and then along vector $b$ from $Q$ to $R$. Norbert Hofer walks
directly from $P$ to $R$. How much farther does Alexander van der
Bellen walk than Norbert Hofer?

\begin{equation}
  \label{eq:uupianai}
a=\left(
  \begin{array}{c}
    17 \\
    -23
  \end{array}\right)\mbox{ and }
b=\left(
  \begin{array}{c}
    26 \\
    -9
  \end{array}\right)
\end{equation}

\end{document}

